### 2023-03-29 response-to-audit-report.md

+                       $ Let "Neutral" (Constant 1)
+                       $ When
+                         [
+                           Case (Deposit party party ada value)
+                             Close
+                         ]
+                         depositDeadline
+                         Close
+                    , Case (Notify $ ValueLT value $ Constant 0)
+                       $ Let "Negative" (Constant 1)
+                       $ When
+                         [
+                           Case (Deposit counterparty party ada value)
+                             Close
+                         ]
+                         depositDeadline
+                         Close
+                    ]
+                    notifyDeadline
+                    Close
+              ]
+              choiceDeadline
+              Close
+      ]
+      initialDeadline
+      Close
+
+
+-- | A wrapper to assist parsing of test cases.
+newtype Map k v = Map {unMap :: [(k, v)]}
+
+
+-- | A function to assist parsing of test cases.
+toAM :: Map k v -> AM.Map k v
+toAM = AM.fromList . unMap
+
+
+-- | A list of test cases and results that should succeed, generated from `Language.Marlowe.FindInputs.getAllInputs`.
+valids :: [(POSIXTime, [TransactionInput], TransactionOutput)]
+valids =
+  [
+    (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 1000},POSIXTime {getPOSIXTime = 1000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = []}, boundValues = toAM $ Map {unMap = []}, minTime = POSIXTime {getPOSIXTime = 1000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 2000},POSIXTime {getPOSIXTime = 2000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = []}, boundValues = toAM $ Map {unMap = []}, minTime = POSIXTime {getPOSIXTime = 2000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 0)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 3000},POSIXTime {getPOSIXTime = 3000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",0)]}, boundValues = toAM $ Map {unMap = []}, minTime = POSIXTime {getPOSIXTime = 3000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 0)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Party" "Counterparty" (Token "" "") 0)]}], TransactionOutput {txOutWarnings = [TransactionNonPositiveDeposit "Counterparty" "Party" (Token "" "") 0], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",0)]}, boundValues = toAM $ Map {unMap = []}, minTime = POSIXTime {getPOSIXTime = 0}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 1)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 4000},POSIXTime {getPOSIXTime = 4000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",1)]}, boundValues = toAM $ Map {unMap = [("Positive",1)]}, minTime = POSIXTime {getPOSIXTime = 4000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 1)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Party" "Counterparty" (Token "" "") 1)]}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000,Payment "Party" (Party "Party") (Token "" "") 1], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",1)]}, boundValues = toAM $ Map {unMap = [("Positive",1)]}, minTime = POSIXTime {getPOSIXTime = 0}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 0)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 4000},POSIXTime {getPOSIXTime = 4000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",0)]}, boundValues = toAM $ Map {unMap = [("Neutral",1)]}, minTime = POSIXTime {getPOSIXTime = 4000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") 0)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Party" "Party" (Token "" "") 0)]}], TransactionOutput {txOutWarnings = [TransactionNonPositiveDeposit "Party" "Party" (Token "" "") 0], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",0)]}, boundValues = toAM $ Map {unMap = [("Neutral",1)]}, minTime = POSIXTime {getPOSIXTime = 0}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") (-1))]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 4000},POSIXTime {getPOSIXTime = 4000}), txInputs = []}], TransactionOutput {txOutWarnings = [], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",-1)]}, boundValues = toAM $ Map {unMap = [("Negative",1)]}, minTime = POSIXTime {getPOSIXTime = 4000}}, txOutContract = Close})
+  , (POSIXTime {getPOSIXTime = 0}, [TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Counterparty" (Token "" "") 2000000)]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IChoice (ChoiceId "Deposit" "Party") (-1))]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput INotify]},TransactionInput {txInterval = (POSIXTime {getPOSIXTime = 0},POSIXTime {getPOSIXTime = 0}), txInputs = [NormalInput (IDeposit "Counterparty" "Party" (Token "" "") (-1))]}], TransactionOutput {txOutWarnings = [TransactionNonPositiveDeposit "Party" "Counterparty" (Token "" "") (-1)], txOutPayments = [Payment "Counterparty" (Party "Counterparty") (Token "" "") 2000000], txOutState = State {accounts = toAM $ Map {unMap = []}, choices = toAM $ Map {unMap = [(ChoiceId "Deposit" "Party",-1)]}, boundValues = toAM $ Map {unMap = [("Negative",1)]}, minTime = POSIXTime {getPOSIXTime = 0}}, txOutContract = Close})
+  ]
+
+
+-- | A list of test cases and results that should fail.
+invalids :: [(POSIXTime, [TransactionInput], TransactionOutput)]
+invalids =
+  [
+  ]
diff --git a/marlowe-test/src/Spec/Marlowe/Semantics/Merkle.hs b/marlowe-test/src/Spec/Marlowe/Semantics/Merkle.hs
index 747c053fa..ebe286cb3 100644
--- a/marlowe-test/src/Spec/Marlowe/Semantics/Merkle.hs
+++ b/marlowe-test/src/Spec/Marlowe/Semantics/Merkle.hs
@@ -14,7 +14,6 @@
 {-# LANGUAGE FlexibleContexts #-}
 {-# LANGUAGE RankNTypes #-}
 {-# LANGUAGE RecordWildCards #-}
-{-# LANGUAGE TupleSections #-}

 module Spec.Marlowe.Semantics.Merkle
diff --git a/marlowe-test/src/Spec/Marlowe/Semantics/Oracle.hs b/marlowe-test/src/Spec/Marlowe/Semantics/Oracle.hs
deleted file mode 100644
index 081e88034..000000000
--- a/marlowe-test/src/Spec/Marlowe/Semantics/Oracle.hs
+++ /dev/null
@@ -1,261 +0,0 @@
------------------------------------------------------------------------------
---
--- Module      :  $Headers
--- License     :  Apache 2.0
---
--- Stability   :  Experimental
--- Portability :  Portable
---
--- | Tests using external semantics oracle.
---
------------------------------------------------------------------------------
-
-
-
-{-# LANGUAGE DeriveGeneric #-}
-{-# LANGUAGE NumericUnderscores #-}
-{-# LANGUAGE OverloadedStrings #-}
-{-# LANGUAGE RecordWildCards #-}
-
-
-module Spec.Marlowe.Semantics.Oracle
-  ( -- * Tests
-    tests
-  ) where
-
-
-import Data.Aeson
-  ( FromJSON(parseJSON)
-  , KeyValue((.=))
-  , ToJSON(toJSON)
-  , Value(Array)
-  , eitherDecode
-  , encode
-  , object
-  , withArray
-  , withObject
-  , (.:)
-  )
-import Data.Aeson.Types (Parser)
-import Data.Function (on)
-import Data.List (sort)
-import Data.String (fromString)
-import Data.Vector ((!))
-import GHC.Generics (Generic)
-import Language.Marlowe.Core.V1.Semantics
-  ( Payment(..)
-  , TransactionInput
-  , TransactionOutput(TransactionOutput, txOutContract, txOutPayments, txOutState, txOutWarnings)
-  , computeTransaction
-  )
-import Language.Marlowe.Core.V1.Semantics.Types (Contract, State(..), Token(Token))
-import Language.Marlowe.FindInputs (getAllInputs)
-import System.Directory (doesFileExist)
-import System.IO
-  (BufferMode(LineBuffering), Handle, IOMode(ReadMode, WriteMode), hGetLine, hPutStrLn, hSetBuffering, openFile)
-import Test.Tasty (TestTree)
-import Test.Tasty.HUnit (assertBool, testCaseSteps)
-
-import qualified Data.ByteString.Lazy.Char8 as LBS8 (pack, unpack)
-import qualified Data.Vector as V (fromList)
-import qualified Language.Marlowe.Extended.V1 as E (Contract(Close), Value(Constant), toCore)
-import qualified PlutusTx.AssocMap as AM (Map, empty, toList)
-
-import qualified Marlowe.Contracts.Escrow as Escrow (escrow)
-import qualified Marlowe.Contracts.Forward as Forward (forward)
-import qualified Marlowe.Contracts.Futures as Futures (future)
-import qualified Marlowe.Contracts.Swap as Swap (swap)
-import qualified Marlowe.Contracts.Trivial as Trivial (trivial)
-import qualified Marlowe.Contracts.ZeroCouponBond as ZeroCouponBond (zeroCouponBond)
-
-
--- | Compare contract execution to the semantics oracle.
---
--- The function reads from a named pipe "orin" and writes to a
--- named pipe "orout". Those same pipes must be connected to the
--- semantics oracle. For example:
---
--- > git clone git@github.com:input-output-hk/marlowe-cardano.git -b 472170bdf77dc9d89bc77861da851d2476b2aa47
--- > nix-shell
--- > cd marlowe-purescript-spec
--- > spago install
--- > spago build
--- > npm install
--- > node index.js <orout >orin
-tests :: TestTree
-tests =
-  testCaseSteps "Semantics Oracle"
-    $ \step ->
-      do
-      okay <- and <$> mapM doesFileExist ["orin", "orout"]
-      if okay
-        then do
-               step "Connecting to semantics oracle . . ."
-               hToOracle   <- openFile "orout" WriteMode
-               hFromOracle <- openFile "orin"  ReadMode
-               hSetBuffering hToOracle   LineBuffering
-               hSetBuffering hFromOracle LineBuffering
-               sequence_
-                 [
-                   do
-                     step $ "Comparing " <> name <> " to oracle . . ."
-                     compareToOracle hToOracle hFromOracle name contract
-                 |
-                   (name, contract) <- contracts
-                 ]
-        else step "No semantics oracle found on pipes \"orin\" and \"orout\"."
-
-
--- | Contracts to be tested.
-contracts :: [(String, E.Contract)]
-contracts =
-  let
-    alice = "Alice"
-    bob = "Bob"
-    charlie = "Charlie"
-    v = E.Constant
-    a = Token "aaaa" "A"
-    b = Token "bbbb" "B"
-    c = Token "cccc" "C"
-  in
-    [
